Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-04-20 paper/current/main.tex
new supporting figures

Given that embeddings capture effective distance between organizations, we can now examine the global structure of scientific mobility.
Because the embeddings are defined in a high-dimensional space, we apply a widely-used dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to visualize the overall structure (Fig.~\ref{fig:projection}a).
Globally, the effect of geography is conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions.

@@

%
% Figure - Hyperparameter performance
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
	\caption{
		\textbf{Larger dimensions, smaller window size improves embedding performance.}
		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters.
		Window size refers to the window, on either side of the target token, to use as context for training.
		Smaller window sizes results in an embedding that explain more of the flux.
		Embedding dimensions refer to the size of the organization vector.
		Larger vectors perform better, though little difference between 200 and 300.
		All variants perform better on same-country pairs of organizations than on all organizations.
		All variants perform worse on different-country pairs on organizations.
		Larger embeddings outperform mid-size embeddings for the different-country case.
	}
	\label{fig:supp:hyperparams}
\end{figure}

@@

@@

@@

%
% Figure - SemAxis By Sector
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching organizations, respectively.
		Grey points correspond to all U.S. universities.
	    	Full organization names listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:supp:semaxis_sectors}
\end{figure}

>>>>

Given that embeddings capture effective distance between organizations, we can now examine the global structure of scientific mobility.
Because the embeddings are defined in a high-dimensional space, we apply a widely-used dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to visualize the overall structure (Fig.~\ref{fig:projection}a).
Globally, the effect of geography is conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than altenrative network visualizations (Fig.~\ref{fig:supp:network_vis}).

@@

%
% Figure - Hyperparameter performance
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
	\caption{
		\textbf{Larger dimensions, smaller window size improves embedding performance.}
		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters.
		Window size refers to the window, on either side of the target token, to use as context for training.
		Smaller window sizes results in an embedding that explain more of the flux.
		Embedding dimensions refer to the size of the organization vector.
		Larger vectors perform better, though little difference between 200 and 300.
		All variants perform better on same-country pairs of organizations than on all organizations.
		All variants perform worse on different-country pairs on organizations.
		Larger embeddings outperform mid-size embeddings for the different-country case.
	}
	\label{fig:supp:cosdot}
\end{figure}

%
% Figure - Dot product and cosine similarity
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/d300_ws1_dot_cosine.pdf}
	\caption{
		\textbf{Cosine distance is correlated with dot product similarity.}
		Calculated as the pairwise cosine distance (x-axis) and dot product similarity (y-axis) between organizational vectors. 
		The two quantities are correlated with $R^{2} = 0.73$. 
		Color indicates frequency of organizations in hex bin. 
		Black dots are the mean dot product similarity for binned sets of embedding similarity and error bars correspond to 95\textsc{th} percentile confidence intervals. 
		Red line is line of best fit.
	}
	\label{fig:supp:hyperparams}
\end{figure}

@@

%
% Figure - Dot product distance
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_dot.pdf}
	\caption{
		\textbf{Personalized page rank with cosine distance.}
		Performance of dot product similarities in explaining and predicting mobility.
		Similarity scores are calculated as the pairwise dot product between organizational vectors. 
		Dot product similarity performs better than geographic distance, though worse than cosine similarity in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
		Red line is line of best fit.
		Black dots are mean flux across binned distances.
		Color indicates frequency of organization pairs within each hex bin.
		Similarly, PPR distance performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$.
	}
	\label{fig:supp:gravity_dot}
\end{figure}

@@

%
% Figure - Global Network Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/co_occur_with_label.pdf}
	\caption{
		\textbf{Visualization of global mobility network.}
		The network demonstrates country-level structure, but not at the detail or the extent of the global UMAP projection (Fig.~\ref{fig:projection}a). 
		Each node corresponds to an organization, whereas  weighted edges (not shown) correspond to the flow of mobile researchers between the two organization.
		Nodes are colored by the country of the organization. 
		Nodes are positioned using the force atlas layout algorithm. 
	}
	\label{fig:supp:proj_newyork}
\end{figure}

@@

%
% Figure - SemAxis By Sector
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching organizations, respectively.
		Grey points correspond to all U.S. universities.
	    	Full organization names listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:supp:network_vis}
\end{figure}
